An efficient feedback calibration algorithm for direct imaging radio telescopes

### 2016-02-23 cal_demo/ms.tex
Add comments to section 3

For our unknown gains, we create a set of random numbers with amplitude $1\pm0.25$, and completely random phase. These are our ``true gains", and we apply them to the frequency-domain simulated antenna electric fields as in equation~\ref{eq:apply_gain}. Our analysis is blind to these values until the end of the process to check accuracy. The gain estimates are initialized with unity, $g^{(0)}_a=1$.

@@

Images created at the beginning of calibration and at the end are shown in figure~\ref{fig:sim_images}. Each image is 10~ms integration, corresponding to all snapshot images created with a given set of gain estimates. The top panel shows the image produced with our initialized unity gains. Because the phases are completely random, the image is essentially noise with the primary beam evident. After 20 iterations, the image is far more clear, shown in the bottom panel. Each of the ten simulated sources are clearly visible, indicated with red circles.

>>>>

For our unknown gains, we create a set of random numbers with amplitude $1\pm0.25$ ({\bf replace with amplitude in range [0.75, 1.25]}), and completely random phase. These are our ``true gains", and we apply them to the frequency-domain simulated antenna electric fields as in equation~\ref{eq:apply_gain}. Our analysis is blind to these values until the end of the process to check accuracy. The gain estimates are initialized with unity, $g^{(0)}_a=1$.

@@

Images created at the beginning of calibration and at the end are shown in figure~\ref{fig:sim_images}. Each image is {\bf obtained over} 10~ms integration, corresponding to all snapshot images created with a given set of gain estimates. The top panel shows the image produced with our initialized unity gains. Because the phases are completely random, the image is essentially noise with the primary beam evident. After 20 iterations, the image is far more clear, shown in the bottom panel. Each of the ten simulated sources are clearly visible, indicated with red circles.
